Are We Reusing Outdated and License-Violating Code from Stack Overflow?

### 2017-02-12 cloneoverflow-latex/cloneoverflow.tex
Updated the license part.

\title{Are We Reusing Outdated and License-Violating Code Snippets from Stack Overflow?}

@@

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

@@

\begin{table}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering.}
	\label{tab:online_clone_pairs}
	\small
%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multicolumn{1}{c|}{Before} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{Cand.} \\ \cline{3-6}
		& \multicolumn{1}{c|}{Filters} & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 88 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 310,803 & & & & & 31,946 \\ 
		\hline
		\multicolumn{7}{l}{\scriptsize{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 85\%$,}} \\
		\multicolumn{7}{l}{\scriptsize{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.}} \\
	\end{tabular} %
%}
\end{table}

@@

To check if our online code clones are outdated, we focused on the 110 QS clone pairs that were cloned from Qualitas to Stack Overflow (see \Cref{tab:classification_good_o}) and compared them with their latest versions. We cloned the latest version of the Qualitas projects from their repositories on 26 September 2016. For each online clone pair, we used the file name of Qualitas clone to search for its latest version. Once we found the file, we located the location of the cloned snippets in the file based on method names. So for Simian clones that may not contain in a single method, we looked further up and down the clone region to get the method name and its nearby methods. We then compared the Stack Overflow snippet to its latest version line-by-line to find if any change has been made to the source code. We also made sure that the changes did not come from modifications maded to Stack Overflow snippets by the posters but from the projects themselves. When we found inconsistent lines between the two versions, we used \texttt{git blame} command to see who modified those lines of code and noted down the details.

\Cref{fig:outdated} shows the findings of outdated online clones on Stack Overflow. We discovered 59 outdated online clone pairs out of 110 pairs. {\small{\texttt{spring}}} and {\small{\texttt{hibernate}}} have the maximum number of 20 outdated pairs, followed by 15 from {\small{\texttt{eclipse}}}, and 12 from {\small{\texttt{hadoop}}}. An example of outdated code in {\small{texttt{hadoop}}}'s {\small{\texttt{WritableComparator.java}}} has already been shown in \Cref{fig:before-after}. We also found a few outdated code which contained heavy modifications. For example, the code snippet in Stack Overflow post 23520731, a copy of {\small{\texttt{SchemaUpdate.java}}} in {\small{\texttt{hibernate}}}, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}). We also found 3 ``dead'' snippets. These snippets did not have their originals in the latest version of the projects anymore. For example, the snippet in Stack Overflow post 3758110, a copy of {\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in {\small{\texttt{spring}}}, was deleted in commit {\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted. %The latest version of Spring does not contain the file anymore.

@@

	\caption{62 QS outdated online clone pairs. Outdated clones are caused (\textit{C}) by modified/added/deleted statements (\textit{sm}), file deletion (\textit{fd}), and method rewriting (\textit{rw}).}

@@

	\begin{tabular}{r|l|c|l|c|p{5.8cm}|r|r|c|c|c}

@@

		No. & SO Post & SO Date & Q project & Ver. & File & Start & End & Q Date & \textit{C} & $C$ Date \\

@@

			1 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjtools/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
			2 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjweaver/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
			3 & 2513183 & 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 113 & 166 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
			4 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 117 & 126 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
			5 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 143 & 165 & 5-Jun-13 & \textit{sm} & 1-Mar-11 \\
			6 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 178 & 187 & 5-Jun-13 & \textit{sm} & 5-Jun-13 \\
			7 & 11861598 & 8-Aug-12 & eclipse-SDK & 4.3 & WizardDialog.java & 377 & 394 & 1-May-13 & \textit{sm} & 21-Jun-13 \\
			8 & 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{sm} & 20-Nov-14 \\
			9 & 801987 & 29-Apr-09 & hadoop & 1.0.0 & StringUtils.java & 40 & 56 & 15-Dec-11 & \textit{sm} & 4-Feb-13 \\
			10 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 275 & 287 & 15-Dec-11 & \textit{sm} & 12-Jun-11 \\
			11 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 289 & 309 & 15-Dec-11 & \textit{sm} & 12-Jun-11 \\
			12 & 14845581 & 13-Feb-13 & hadoop & 1.0.0 & JobSubmissionFiles.java & 46 & 55 & 15-Dec-11 & \textit{sm} & 25-Jun-12 \\
			13 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapred/../LineRecordReader.java & 47 & 60 & 15-Dec-11 & \textit{rw} & 25-Jul-11 \\
			14 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapreduce/../LineRecordReader.java & 41 & 54 & 15-Dec-11 & \textit{rw} & 25-Jul-11 \\
			15 & 15168494 & 24-Feb-14 & hibernate & 4.2.2 & ConnectionProviderInitiator.java & 65 & 93 & 22-May-13 & \textit{sm} & 26-Apr-13 \\
			16 & 24924255 & 24-Jul-14 & hibernate & 4.2.2 & Example.java & 224 & 243 & 22-May-13 & \textit{sm} & 23-Apr-13 \\
			17 & 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{sm} & 5-Feb-16 \\
			18 & 8257554 & 26-Nov-11 & hibernate & 4.2.2 & SettingsFactory.java & 244 & 255 & 22-May-13 & \textit{fd} & 11-Mar-11 \\
			19 & 23967852 & 31-Apr-14 & hibernate & 4.2.2 & SQLServer2005LimitHandler.java & 43 & 61 & 22-May-13 & \textit{sm} & 11-May-16 \\
			20 & 19298607 & 10-Oct-13 & hibernate & 4.2.2 & Oracle9iDialect.java & 23 & 32 & 22-May-13 & \textit{sm} & 12-Apr-15 \\
			21 & 10031897 & 5-Apr-12 & hibernate & 4.2.2 & AliasToBeanResultTransformer.java & 44 & 61 & 22-May-13 & \textit{sm} & 4-Jun-15 \\ 
			22 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 982 & 998 & 31-May-10 & \textit{sm} & 17-Apr-08 \\
			23 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{fd} & 20-May-11 \\
			24 & 12936580 & 17-Oct-12 & jfreechart & 1.0.13 & AbstractXYItemRenderer.java & 532 & 569 & 20-Apr-09 & \textit{sm} & 16-Jan-16 \\
			25 & 16058183 & 17-Apr-13 & jfreechart & 1.0.13 & KeyToGroupMap.java & 18 & 30 & 20-Apr-09 & \textit{sm} & 29-Jun-07 \\
			26 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 502 & 520 & 20-Apr-09 & \textit{sm} & 2-Jun-08 \\
			27 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 522 & 536 & 20-Apr-09 & \textit{sm} & 22-Nov-13 \\
			28 & 6722760 & 17-Jul-11 & jgraph & 5.13.0.0 & HelloWorld.java (3 overlaps)  & 14 & 37 & 25-Sep-09 & \textit{rw} & 13-Apr-14 \\
			31 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 106 & 117 & 20-Jun-08 & \textit{sm} & 13-Apr-10 \\
			32 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 158 & 172 & 20-Jun-08 & \textit{sm} & 29-Nov-15 \\
			33 & 23586872 & 31-May-14 & junit & 4.11 & Assert.java & 33 & 52 & 11-Oct-12 & \textit{sm} & 12-May-15 \\
			34 & 7504040 & 29-Sep-11 & junit & 4.11 & ExternalResource.java (3 overlaps) & 4 & 23 & 11-Oct-12 & \textit{sm} & 25-Jun-16 \\
			37 & 8802082 & 10-Jan-12 & junit & 4.11 & ExpectException.java (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{sm} & 25-May-14 \\
			39 & 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{rw} & 26-Jun-13 \\
			40 & 20913543 & 6-Jan-14 & spring & 3.0.5  & AutowireUtils.java & 32 & 42 & 20-Oct-10 & \textit{sm} & 28-Oct-14 \\
			41 & 18623736 & 4-Sep-13 & spring & 3.0.5  & CustomCollectionEditor.java & 33 & 71 & 20-Oct-10 & \textit{sm} & 21-Nov-13 \\
			42 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 169 & 185 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
			43 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 186 & 197 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
			44 & 20421869 & 6-Dec-13 & spring & 3.0.5  & ClassPathScanningCandidateComponent\newline Provider.java (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{rw} & 12-Aug-16 \\
			46 & 3751463 & 20-Sep-10 & spring & 3.0.5  & ScheduledTasksBeanDefinitionParser.java & 42 & 52 & 20-Oct-10 & \textit{sm} & 21-May-12 \\
			47 & 6149818 & 27-May-11 & spring & 3.0.5  & DefaultPropertiesPersister.java & 69 & 80 & 20-Oct-10 & \textit{sm} & 19-Mar-13 \\
			48 & 10952561 & 8-Jun-12 & spring & 3.0.5  & HibernateTemplate.java & 761 & 769 & 20-Oct-10 & \textit{sm} & 9-May-15 \\
			49 & 10952561 & 8-Jun-12 & spring & 3.0.5  & Jaxb2Marshaller.java & 253 & 269 & 20-Oct-10 & \textit{sm} & 28-Aug-12 \\
			50 & 20996373 & 8-Jan-14 & spring & 3.0.5  & test/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 18-Dec-08 \\
			51 & 20996373 & 8-Jan-14 & spring & 3.0.5  & web/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
			52 & 20996373 & 8-Jan-14 & spring & 3.0.5  & servlet/../ DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
			53 & 5660519 & 15-Apr-11 & spring & 3.0.5 & AnnotationMethodHandlerExceptionResolver.java & 224 & 233 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
			54 & 4781746 & 24-Jan-11 & spring & 3.0.5  & DispatcherServlet.java & 91 & 103 & 20-Oct-10 & \textit{sm} & 8-Aug-11 \\
			55 & 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
			56 & 9003314 & 25-Jan-12 & spring & 3.0.5  & WebDataBinder.java & 95 & 108 & 20-Oct-10 & \textit{fd} & 15-Aug-10 \\
			57 & 14019840 & 24-Dec-12 & struts2 & 2.2.1  & DefaultActionMapper.java & 128 & 144 & 17-Jul-10 & \textit{sm} & 18-Oct-13 \\
			58 & 15131432 & 28-Feb-13 & struts2 & 2.2.1  & FreemarkerManager.java & 163 & 177 & 17-Jul-10 & \textit{sm} & 28-Oct-13 \\
			59 & 15110171 & 27-Feb-13 & struts2 & 2.2.1  & StringLengthFieldValidator.java & 25 & 42 & 17-Jul-10 & \textit{sm} & 15-Jun-15 \\
			60 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & BasicAuthenticator.java (2 overlaps) & 25 & 73 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
			62 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
			63 & 24404964 & 25-Jun-14 & tomcat & 7.0.2  & CoyoteAdapter.java & 543 & 553 & 4-Aug-10 & \textit{sm} & 25-Sep-14 \\
			64 & 10289462 & 23-Apr-12 & tomcat & 7.0.2  & JspRuntimeLibrary.java & 252 & 296 & 4-Aug-10 & \textit{sm} & 12-Sep-12 \\

>>>>

\title{Are We Reusing Outdated and License-Violating Code from Stack Overflow?}

@@

\maketitle

\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

@@

\begin{table}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering.}
	\label{tab:online_clone_pairs}
	\small
%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multicolumn{1}{c|}{Before} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{Cand.} \\ \cline{3-6}
		& \multicolumn{1}{c|}{Filters} & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 88 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 310,803 & & & & & 31,946 \\ 
		\hline
		\multicolumn{7}{l}{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 85\%$,} \\
		\multicolumn{7}{l}{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.} \\
	\end{tabular} %
%}
\end{table}

@@

To check if our online code clones are outdated, we focused on the 112 QS clone pairs that were cloned from Qualitas to Stack Overflow (see \Cref{tab:classification_good_o}) and compared them with their latest versions. We cloned the latest version of the Qualitas projects from their repositories on 26 September 2016. For each online clone pair, we used the file name of Qualitas clone to search for its latest version. Once we found the file, we located the location of the cloned snippets in the file based on method names. So for Simian clones that may not contain in a single method, we looked further up and down the clone region to get the method name and its nearby methods. We then compared the Stack Overflow snippet to its latest version line-by-line to find if any change has been made to the source code. We also made sure that the changes did not come from modifications maded to Stack Overflow snippets by the posters but from the projects themselves. When we found inconsistent lines between the two versions, we used \texttt{git blame} command to see who modified those lines of code and noted down the details.

\Cref{fig:outdated} shows the findings of outdated online clones on Stack Overflow. We discovered 64 outdated online clone pairs out of 112 pairs. {\small{\texttt{spring}}} and {\small{\texttt{hibernate}}} have the maximum number of 20 outdated pairs, followed by 15 from {\small{\texttt{eclipse}}}, and 12 from {\small{\texttt{hadoop}}}. An example of outdated code in {\small{texttt{hadoop}}}'s {\small{\texttt{WritableComparator.java}}} has already been shown in \Cref{fig:before-after}. We also found a few outdated code which contained heavy modifications. For example, the code snippet in Stack Overflow post 23520731, a copy of {\small{\texttt{SchemaUpdate.java}}} in {\small{\texttt{hibernate}}}, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}). In the 64 outdate pairs, we found 5 of them to be ``dead'' snippets. These snippets did not have their originals in the latest version of the projects anymore. For example, the snippet in Stack Overflow post 3758110, a copy of {\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in {\small{\texttt{spring}}}, was deleted in commit {\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted. %The latest version of Spring does not contain the file anymore.

@@

	\caption{62 QS outdated online clone pairs. Outdated clones are caused by modified/added/deleted statements (\textit{S}), file deletion (\textit{D}), and method rewriting (\textit{R}).}

@@

	\begin{tabular}{r|l|l|l|l|p{5.2cm}|r|r|l|c|l}

@@

		\multirow{2}{*}{No.} & \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ \cline{2-11}
		& Post & Date & Project & Ver. & File & Start & End & Date & Type & Date \\

@@

			1 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjtools/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{S} & 8-Sep-15 \\
			2 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjweaver/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{S} & 8-Sep-15 \\
			3 & 2513183 & 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 113 & 166 & 5-Jun-13 & \textit{S} & 17-Mar-15 \\
			4 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 117 & 126 & 5-Jun-13 & \textit{S} & 17-Mar-15 \\
			5 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 143 & 165 & 5-Jun-13 & \textit{S} & 1-Mar-11 \\
			6 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 178 & 187 & 5-Jun-13 & \textit{S} & 5-Jun-13 \\
			7 & 11861598 & 8-Aug-12 & eclipse-SDK & 4.3 & WizardDialog.java & 377 & 394 & 1-May-13 & \textit{S} & 21-Jun-13 \\
			8 & 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
			9 & 801987 & 29-Apr-09 & hadoop & 1.0.0 & StringUtils.java & 40 & 56 & 15-Dec-11 & \textit{S} & 4-Feb-13 \\
			10 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 275 & 287 & 15-Dec-11 & \textit{S} & 12-Jun-11 \\
			11 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 289 & 309 & 15-Dec-11 & \textit{S} & 12-Jun-11 \\
			12 & 14845581 & 13-Feb-13 & hadoop & 1.0.0 & JobSubmissionFiles.java & 46 & 55 & 15-Dec-11 & \textit{S} & 25-Jun-12 \\
			13 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapred/../LineRecordReader.java & 47 & 60 & 15-Dec-11 & \textit{R} & 25-Jul-11 \\
			14 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapreduce/../LineRecordReader.java & 41 & 54 & 15-Dec-11 & \textit{R} & 25-Jul-11 \\
			15 & 15168494 & 24-Feb-14 & hibernate & 4.2.2 & ConnectionProviderInitiator.java & 65 & 93 & 22-May-13 & \textit{S} & 26-Apr-13 \\
			16 & 24924255 & 24-Jul-14 & hibernate & 4.2.2 & Example.java & 224 & 243 & 22-May-13 & \textit{S} & 23-Apr-13 \\
			17 & 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
			18 & 8257554 & 26-Nov-11 & hibernate & 4.2.2 & SettingsFactory.java & 244 & 255 & 22-May-13 & \textit{D} & 11-Mar-11 \\
			19 & 23967852 & 31-Apr-14 & hibernate & 4.2.2 & SQLServer2005LimitHandler.java & 43 & 61 & 22-May-13 & \textit{S} & 11-May-16 \\
			20 & 19298607 & 10-Oct-13 & hibernate & 4.2.2 & Oracle9iDialect.java & 23 & 32 & 22-May-13 & \textit{S} & 12-Apr-15 \\
			21 & 10031897 & 5-Apr-12 & hibernate & 4.2.2 & AliasToBeanResultTransformer.java & 44 & 61 & 22-May-13 & \textit{S} & 4-Jun-15 \\ 
			22 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 982 & 998 & 31-May-10 & \textit{S} & 17-Apr-08 \\
			23 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
			24 & 12936580 & 17-Oct-12 & jfreechart & 1.0.13 & AbstractXYItemRenderer.java & 532 & 569 & 20-Apr-09 & \textit{S} & 16-Jan-16 \\
			25 & 16058183 & 17-Apr-13 & jfreechart & 1.0.13 & KeyToGroupMap.java & 18 & 30 & 20-Apr-09 & \textit{S} & 29-Jun-07 \\
			26 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 502 & 520 & 20-Apr-09 & \textit{S} & 2-Jun-08 \\
			27 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 522 & 536 & 20-Apr-09 & \textit{S} & 22-Nov-13 \\
			28 & 6722760 & 17-Jul-11 & jgraph & 5.13.0.0 & HelloWorld.java (3 overlaps)  & 14 & 37 & 25-Sep-09 & \textit{R} & 13-Apr-14 \\
			31 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 106 & 117 & 20-Jun-08 & \textit{S} & 13-Apr-10 \\
			32 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 158 & 172 & 20-Jun-08 & \textit{S} & 29-Nov-15 \\
			33 & 23586872 & 31-May-14 & junit & 4.11 & Assert.java & 33 & 52 & 11-Oct-12 & \textit{S} & 12-May-15 \\
			34 & 7504040 & 29-Sep-11 & junit & 4.11 & ExternalResource.java (3 overlaps) & 4 & 23 & 11-Oct-12 & \textit{S} & 25-Jun-16 \\
			37 & 8802082 & 10-Jan-12 & junit & 4.11 & ExpectException.java (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{S} & 25-May-14 \\
			39 & 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
			40 & 20913543 & 6-Jan-14 & spring & 3.0.5  & AutowireUtils.java & 32 & 42 & 20-Oct-10 & \textit{S} & 28-Oct-14 \\
			41 & 18623736 & 4-Sep-13 & spring & 3.0.5  & CustomCollectionEditor.java & 33 & 71 & 20-Oct-10 & \textit{S} & 21-Nov-13 \\
			42 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 169 & 185 & 20-Oct-10 & \textit{S} & 6-Oct-14 \\
			43 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 186 & 197 & 20-Oct-10 & \textit{S} & 6-Oct-14 \\
			44 & 20421869 & 6-Dec-13 & spring & 3.0.5  & ClassPathScanningCandidateComponent\newline Provider.java (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{R} & 12-Aug-16 \\
			46 & 3751463 & 20-Sep-10 & spring & 3.0.5  & ScheduledTasksBeanDefinitionParser.java & 42 & 52 & 20-Oct-10 & \textit{S} & 21-May-12 \\
			47 & 6149818 & 27-May-11 & spring & 3.0.5  & DefaultPropertiesPersister.java & 69 & 80 & 20-Oct-10 & \textit{S} & 19-Mar-13 \\
			48 & 10952561 & 8-Jun-12 & spring & 3.0.5  & HibernateTemplate.java & 761 & 769 & 20-Oct-10 & \textit{S} & 9-May-15 \\
			49 & 10952561 & 8-Jun-12 & spring & 3.0.5  & Jaxb2Marshaller.java & 253 & 269 & 20-Oct-10 & \textit{S} & 28-Aug-12 \\
			50 & 20996373 & 8-Jan-14 & spring & 3.0.5  & test/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{S} & 18-Dec-08 \\
			51 & 20996373 & 8-Jan-14 & spring & 3.0.5  & web/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{S} & 15-Jul-16 \\
			52 & 20996373 & 8-Jan-14 & spring & 3.0.5  & servlet/../ DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{S} & 15-Jul-16 \\
			53 & 5660519 & 15-Apr-11 & spring & 3.0.5 & AnnotationMethodHandlerException\newline Resolver.java & 224 & 233 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
			54 & 4781746 & 24-Jan-11 & spring & 3.0.5  & DispatcherServlet.java & 91 & 103 & 20-Oct-10 & \textit{S} & 8-Aug-11 \\
			55 & 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
			56 & 9003314 & 25-Jan-12 & spring & 3.0.5  & WebDataBinder.java & 95 & 108 & 20-Oct-10 & \textit{S} & 15-Aug-10 \\
			57 & 14019840 & 24-Dec-12 & struts2 & 2.2.1  & DefaultActionMapper.java & 128 & 144 & 17-Jul-10 & \textit{S} & 18-Oct-13 \\
			58 & 15131432 & 28-Feb-13 & struts2 & 2.2.1  & FreemarkerManager.java & 163 & 177 & 17-Jul-10 & \textit{S} & 28-Oct-13 \\
			59 & 15110171 & 27-Feb-13 & struts2 & 2.2.1  & StringLengthFieldValidator.java & 25 & 42 & 17-Jul-10 & \textit{S} & 15-Jun-15 \\
			60 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & BasicAuthenticator.java (2 overlaps) & 25 & 73 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
			62 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
			63 & 24404964 & 25-Jun-14 & tomcat & 7.0.2  & CoyoteAdapter.java & 543 & 553 & 4-Aug-10 & \textit{S} & 25-Sep-14 \\
			64 & 10289462 & 23-Apr-12 & tomcat & 7.0.2  & JspRuntimeLibrary.java & 252 & 296 & 4-Aug-10 & \textit{S} & 12-Sep-12 \\
